### 2020-06-04 2020/phd_midterm_report/report.tex
spelling error

\section*{Other research}
\subsection*{Semantic similarity}
\cite{pham18fixing} proposed a method to predict the semantic similarity between 2 sentences from 2 different languages. The method is used in the context of filtering noisy parallel corpora such as Paracrawl. The method was implemented for corpus filtering shared task  \cite{koehn18findings}. \cite{pham18fixing} used a siamese network to encode a bilingual pair of sentences whose embedding is used to compute the semantic similarity by cosine similarity. The training of the network is done by optimizing the aggregation of soft word alignment scores between 2 sentences. To avoid being over-fitted by positive examples in which every sentence pair is correctly matched, we proposed to use the same amount of artificial negative examples in which words are randomly removed or added and changed in several positions.
\section*{Working plan}
\begin{itemize}
	\item Completing work on residual adapters and submission to WMT 2020 in the end of July 2020.
	\item Completing system submission to Machine Translation Robustness task of WMT 2020 in the end of July 2020.
	\item Completing work on contextualized Machine Translation with Systran's team in the end of July 2020.
	\item Completing work on Multi-source Adaptation between September - December 2020
	\item Completing work on BPE-vocabulary's transfer learning effect between January and March 2021.
	\item 
\end{itemize}
\bibliography{bibliography}
\bibliographystyle{apa-good}
\end{document}

>>>>

\section*{Other research}
\subsection*{Semantic similarity}
\cite{pham18fixing} proposed a method to predict the semantic similarity between 2 sentences from 2 different languages. The method is used in the context of filtering noisy parallel corpora such as Paracrawl. The method was implemented for corpus filtering shared task  \cite{koehn18findings}. \cite{pham18fixing} used a siamese network to encode a bilingual pair of sentences whose embedding is used to compute the semantic similarity by cosine similarity. The training of the network is done by optimizing the aggregation of soft word alignment scores between 2 sentences. To avoid being over-fitted by positive examples in which every sentence pair is correctly matched, we proposed to use the same amount of artificial negative examples in which words are randomly removed or added and changed in several positions.
\section*{Provisional planning}
\begin{itemize}
	\item Completing work on residual adapters and submission to WMT 2020 at the end of July 2020.
	\item Completing system submission to Machine Translation Robustness task of WMT 2020 at the end of July 2020.
	\item Completing work on contextualized Machine Translation with Systran's team at the end of July 2020.
	\item Completing work on Multi-source Adaptation between August - December 2020
	\item Completing work on BPE-vocabulary's transfer learning effect between January and April 2021.
\end{itemize}
\bibliography{bibliography}
\bibliographystyle{apa-good}
\end{document}
